%%% A template to produce a nice-looking Curriculum Vitae.
%%% Original : Kieran Healy <kjhealy@gmail.com>
%%% Customised : Adrian Ionita <adrian@ionita.me>
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
\usepackage{fontawesome,url}

\usepackage{geometry}
\geometry{
  rmargin=3.0cm,
  lmargin=3.0cm,
  tmargin=2.3cm,
  bmargin=2.3cm,
  marginpar=1.8cm,
}


%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Adrian Ionita}
\def\mycoauthor{Kieran Healy}
\def\mytitle{Curriculum Vitae}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myemail{adrian@ionita.me}
\def\myweb{https://github.com/iceiony}
\def\myphone{0797 187 0684}
\def\mytwitter{@iceiony}
\def\mylinkedin{https://uk.linkedin.com/in/adrian-ionita-6a923129}
\def\myaddress{London / Brighton, UK}
\def\myversion{}
\def\myrevision{}


\date{} % not used (revision control instead)
\def\mykeywords{Adrian, Ionita, Adrian Ionita, Vitae, CV, Resume, DataScience}

\newenvironment{itemize*}{%
  \renewcommand\labelitemi{\textbullet}
  \footnotesize
  \begin{itemize}%
    \setlength{\itemsep}{0pt}}%
  {\end{itemize}
}

\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro}
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]{Unit-Medium}
\setmonofont[Mapping=tex-text,Scale=0.72]{PragmataPro} 

\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

\newfontface\contactblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Minion Pro Medium Caption}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
%\begin{minipage}[t]{2.95in}
% \flushright {\footnotesize 
% \href{http://github.com/iceiony}{Iceiony Ltd}, \\ London \\ UK }  
%
%\end{minipage}
%\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.3in}
  \flushright \footnotesize  \contactblock \myphone \, \faPhone \\ 
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\scriptsize  \texttt{\href{\mylinkedin}{\myauthor}} \, \faLinkedinSquare }  \\ 
  {\scriptsize  \texttt{\href{\myweb}{\myweb}} \, \faGithub}
  {\scriptsize  \texttt{\href{\myaddress}{\myaddress}} \, \faMapMarker} \\
  %{\scriptsize  \texttt{\href{http://twitter.com/iceiony}{\mytwitter}} \, \faTwitter }  \\ 
\end{minipage}

{\vskip -0.8cm}
\noindent{\Huge\scheader \textsc{adrian ionita}}
\reversemarginpar

\bigskip      
\medskip

\hyphenpenalty 10000
\marginhead{\sffamily Profile}
\noindent\emph{Data science engineer focused on computational modeling, with a strong background in software engineering and a deep understanding of the scientific and development challenges faced when building machine learning systems.
I am able to support companies in data science tasks, develop research concepts and turn them into production code; recognized for a keen ability to engage with stakeholders, accurately discerning their true needs through attentive listening and insightful questioning.
My approach ensures the delivery of solutions that are technically sound and highly relevant, thereby empowering organizations to meet their objectives effectively.
}

\bigskip

\marginhead{\sffamily Skills}

\ind Programming:

\ind \hspace{0.354in} \textbf{Python}, \textbf{R}, \textbf{C++}, \textbf{JavaScript}, Test Driven Development (TDD), Docker, Azure, AWS, PySpark, SQL, Graph Databases, MATLAB, C\#, CUDA

\ind Data Science:

\ind \hspace{0.354in} \textbf{Imbalanced Learning}, Algorithms, Language Models, Anomaly Detection, Entity Resolution,
    Monte Carlo Markov Chains, Bayesian Methods, Particle Filters,
    Cluster Analysis, Principal Component Analysis, Independent Component Analysis, Fourier Domains

\ind Machine Learning:

\ind \hspace{0.354in} \textbf{Natural Language Processing} (NLP), \textbf{Deep Learning} (Classification \& Regression), \textbf{Decision Trees / Random Forests},
    RNN, RBF Networks, SOM, Committee Machines, Reinforcement Learning, Improving Generalisation \& Training Speed, PyTorch, Dynet

\bigskip
 
\marginhead{\sffamily Experience}

\normalsize
\medskip
\ind Quant Developer, Iceiony LTD - \emph{founder} \hfill Apr 2025 - Current
\begin{itemize*}
  \item Building a business applying data science techniques to crypto asset trading.
  \item Developing volatility based trading algorithms that acts on high price fluctuations.
  \item Algorithmically determining the optimal trading points for historic data. 
  \item Predicting price direction from orderbook derived metrics.
  \item Building backtesting and data gathering frameworks to play back historic events executing the same code as production.
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: Python, R, C++, Neural Networks, algorithms }

\normalsize
\medskip
\ind Data Scientist / Engineer, SecureCloud+ - \emph{contract} \hfill Jan 2025 - Mar 2025
\begin{itemize*}
    \item Designing the system architecture for a product, linking information across public sources of data at scale and with a strict focus on operational security.
    \item Developing data cleanup and entity resolution to identify people and companies across different data sources.
    \item Collaborating on product design and feasibility, helping design the pitch deck to ultimately win the client's interest.
    \item Coordinating team members to deliver a useful solution to the end client's needs, whilst meeting the company's own objectives for a strategic platform. 
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: Python, Software Architecture, LLMs integration (extraction and translation), Entity Resolution, PySpark}

\normalsize
\medskip
\ind Data Scientist / Engineer, Programable.io (via SWBI) - \emph{contract} \hfill Nov 2023 - Nov 2024
\begin{itemize*}
    \item Developing an insurance fraud detection system, leveraging AI/ML to find more likely cases of fraud.
    \item Contributing to the product design by leveraging the art of the possible in AI/ML to enhance the end user productivity.
    \item Exposing prediction reasoning to help investigators understand the model's decision making.
    \item Simplifying graph representations of claims to help investigators find collusion and relations to past cases of fraud. 
    \item Predicting the duration of investigations to prioritise cases by the best financial outcome.
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: Python, TDD, LLMs (fraud explanation), Information Theory, Network Graphs, Entity Resolution}

\newpage

\normalsize
\medskip
\ind Data Scientist, EDF Trading - \emph{contract} \hfill Nov 2021 - Nov 2023
\begin{itemize*}
    \item Developing trade anomaly detection algorithm, helping company satisfy compliance and regulatory obligations.
    \item Developing systems, tools and NLP algorithms for extracting pricing information from emails, eliminating time waste from manual retrieval. 
    \item Deriving, from raw trade data (i.e. level 3), the exact logic to calculate price candles, saving ~£100k / year in licensing.
    \item Implementing liquidity algorithm for a more a representative view of the market.
    \item Developing prediction algorithm for next day's price correlations (96.5\% accuracy); to estimate future profit and loss. 
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: Python, JavaScript, Flask, Docker, TDD, NLP, LLM chatbots, Random Forests, RNN}

\normalsize
\medskip
\ind R Developer, LLOYDS (via EPAM) - \emph{contract} \hfill Mar 2020 - Oct 2021
\begin{itemize*}
    \item Supporting the actuaries modelling central capital, in the smooth migration of their systems to Azure.
    \item Optimising R functionality to bring large performance improvements (10x) by optimising data access in Azure. 
    \item Training actuaries on R best practices, improving the reliability of their code and day to day operations.
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: R, Rcpp, C++, SQL, RSConnect, Tidyverse, TDD}

\normalsize
\medskip
\ind R Developer, UBS (via Accenture) - \emph{contract} \hfill Jun 2019 - Feb 2020
\begin{itemize*}
    \item Onboarding risk models into simulation platform ensuring reliable operation for regulatory runs.
    \item Setting up code base for continuous integration and deployment leading to a streamlined development process.
    \item Adapting code for execution at scale using SparkR.
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: R, CI/CD, SparkR, TDD}

\normalsize
\medskip
\ind Data Scientist NLP, EDF Energy - \emph{contract} \hfill Dec 2018 - May 2019
\begin{itemize*}
    \item Consulting the business on AI/ML capabilities and lesser known limitations, shaping long term AI strategies
    \item Identifying value opportunities from applied data science, and language processing automation
    \item Delivering insights into customer queries and complaints, guiding business focus to high volume chat-bot cases
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: Python, Chatbots, LDA topic modeling, CorEx topic modeling, Neural Network Classification, TDD }

\normalsize
\medskip

\ind Further Employment History Available on \href{https://uk.linkedin.com/in/adrian-ionita-6a923129}{LinkedIn} \hfill 2010 - 2016

\medskip
\marginhead{\sffamily Projects}

\normalsize
\medskip
\ind Semantic Representation In Human Language \hfill Sep 2016 - Jul 2021
\begin{itemize*}
  \item Developing custom sentence tokenising, enabling reuse across non-english languages
  \item Researching unsupervised training technique for language structure and semantic representation
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: R, Python, Deep Learning (RNN), PyTorch, Dynet, C++}

\normalsize
\medskip
\ind Efficient input sampling for determining minimum viable data \hfill Jan 2018 - Apr 2018
\begin{itemize*}
  \item Designing algorithm for a small data set, which determines the miminimum number of records to form a representative view of the input space.
  \item Developing Bayesian inference technique to estimate the minimum viable records needed for training a model proposition.
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: Python, Bayesian Methods / Probabilistic Programming}

\normalsize
\medskip
\ind Fuel Savings Prediction Model \hfill Jan 2017 - May 2017
\begin{itemize*}
  \item Designing statistical model that estimates fuel and repair savings from optimal tyre inflation for fleets of vehicles
  \item Guiding junior analyst in model implementation, teaching good code practices
\end{itemize*}
\ind \hspace{0.35in} \footnotesize \emph{Key Skills: R, Monte Carlo Markov Chain} \normalsize

\bigskip
\medskip
\marginhead{\sffamily Education}

\ind University Of Birmingham (UK) 
\footnotesize 
\begin{itemize}
    \item \textbf{2015-2016:} \emph{MSc. Computational Neuroscience and Cognitive Robotics} - \textbf{distinction}
    \item \textbf{2009-2010:} \emph{MSc. Computer Security} - \textbf{distinction}
\end{itemize}
\normalsize

\ind University Of Bucharest (Romania) 
\footnotesize 
\begin{itemize}
    \item \textbf{2006-2009:} \emph{BSc. Computer Science} - equivalent \textbf{first class honours}
\end{itemize}
\normalsize

\ind National Center For Excellence (Romania) 

\footnotesize 
\begin{itemize}
    \item \textbf{2006:} \emph{Diploma for Excellence in Computer Science}
\end{itemize}
\normalsize

\end{document}
